Instant Continuation Marks--Just Add $\lambda$

### 2012-10-09 paper.tex
Better example intro.

Consider the \cm\ program \scheme|(wcm 0 ((lambda (x) (wcm x (ccm))) 1))| which reduces as
\begin{schemedisplay}
(wcm 0 ((lambda (x) (wcm x (ccm))) 1))
(wcm 0 (wcm 1 (ccm)))
(wcm 1 (ccm))
(wcm 1 (lambda (z) ((z 1) (lambda (x) (lambda (y) y)))))
(lambda (z) ((z 1) (lambda (x) (lambda (y) y))))
\end{schemedisplay}
and transforms as
\begin{schemedisplay}
Ch[(wcm 0 ((lambda (x) (wcm x (ccm))) 1))]

>>>>

To better illustrate what the transformation does, we step through the reduction of a program which exhibits its more interesting aspects. One \cm\ program suited to this purpose is \scheme|(wcm 0 ((lambda (x) (wcm x (ccm))) 1))|. It reduces according to \cm\ semantics as
\begin{schemedisplay}
(wcm 0 ((lambda (x) (wcm x (ccm))) 1))
(wcm 0 (wcm 1 (ccm)))
(wcm 1 (ccm))
(wcm 1 (lambda (z) ((z 1) (lambda (x) (lambda (y) y)))))
(lambda (z) ((z 1) (lambda (x) (lambda (y) y))))
\end{schemedisplay}

Now consider the transformation of the same program. We apply the transformation just-in-time as we reduce which has the effect of reducing term size and promoting clarity.
\begin{schemedisplay}
Ch[(wcm 0 ((lambda (x) (wcm x (ccm))) 1))]
